Membrane-localized Keratin-14 Promotes Invasion\thanks{Supported by organization x.}

### 2018-12-07 docs/01_paper/paper.tex
Added authors and edited abstract

%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{comment}
\usepackage{xcolor}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Membrane-localized Keratin-14 Promotes Invasion\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author \inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Johns Hopkins University
\url{http://www} \and
Other\\
\email{\{bla,blu\}@jhu.edu}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Metastasis is the main predictor of outcome for patients with cancer, yet the molecular mechanism driving invasive phenotypes is not well understood. Keratin 14 (K14) is a known molecular biomarker that is correlated with poor outcomes in breast cancer patients. In this study, we apply our automated computer model that quantifies the invasive potential of tumors to characterize K14 expression as it relates to invasion. We test the hypothesis that K14 is directly correlated to invasion versus the alternative hypothesis that size is the main predictor. We used two different transgenic mice (PyMT and C3(1)-Tag) as our breast cancer tumor models. Organoids were generated from these mice, and each organoid had a corresponding differential interference contrast image, K14 image, and an invasive potential score generated using our automated system. The parameters assessed include the following: entire K14 expression, peripheral K14 expression (edges of the organoid), central K14 expression (center of the organoid), and organoid size. Peripheral K14 expression showed the strongest correlation with invasion scores for both types of transgenic mice. The results suggest that K14 expression in cells located in the periphery may be an important marker of invasion.

\keywords{Metastasis \and Tumor Invasion \and Keratin 14 \and Spectral Analysis \and ...}
\end{abstract}
%
%
%
\section{Introduction}

@@

\section {Methods}

Fig. 0: Make figure showing the 'pipeline'.

\textcolor{blue}{
\begin{itemize}
    \item Experimental protocol. Ask Veena to write this part.\\ 
        100-300 organoids from 4 mice.
    \item Image acquisition and organoid periphery. Veena.\\
        Use ImageJ to mark the periphery of the organoids from DIC microscope images.
    \item Image segmentation. Andrei to write about convolution kernel.
    \item Spectral score. Reference Joel's paper. Disclose scripts?
\end{itemize}
}

\subsection{Data acquisition}

@@

\subsection{Spectral Analysis}
A method described in REF.\\
Able to distinguish quantitative phenotypes.

\subsection{Convolution kernel}
ANDREI

\subsection{Correlation Analysis}

\begin{figure}
\includegraphics[width=\textwidth]{Image1.pdf}
\caption{Displays the K14 Image, DIC image, Bounday and spectral power analysis plots for three different organoids. \textcolor{red}{Axis font needs to be bigger. Y-axis in spectral score should all be the same and we can probably skip column 2.}} \label{fig1}
\end{figure}

\section{Results}

\begin{table}
\caption{Peripheral K14 explains correlates with invasive potential the best.}\label{tab1}
		\centering
		\resizebox{0.8\textwidth}{!}{
		 \begin{tabular}{||l c c c c||}
			\hline
			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
			 \hline
			 Organoids (PyMMT mice) & 	1 & 2 & 3 & 4 \\ [0.5ex]
			 \hline\hline
			  \textbf{Peripheral sum K14} & \textbf{0.39} & \textbf{0.43} & \textbf{0.29} & \textbf{0.123} \\
			 \hline
			 Centeral sum K14 & 0.21 & 0.19 & 0.11 & 0.010 \\
			 \hline
			 Entire sum K14 & 0.22 & 0.22 & 0.12 & 0.013 \\
			 \hline
%			 K14 Mean & 0.02 & 0.04 & 0.03 \\ [1ex]
%			 \hline
			Organoid size & 0.27 & 0.33 & 0.27 & 0.076 \\
			 \hline
		\end{tabular}
		}
\end{table}

\begin{table}
\caption{Peripheral K14 explains correlates with invasive potential the best.}\label{tab1}
		\centering
		\resizebox{0.8\textwidth}{!}{
		 \begin{tabular}{||l c c c c||}
			\hline
			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
			 \hline
			 Organoids (C3(1)tag mice) & 1 & 2 & 3 & 4  \\ [0.5ex]
			 \hline\hline
			  \textbf{Peripheral sum K14} & \textbf{0.11} & \textbf{0.25} & 0.06 & 0.03 \\
			 \hline
			 Centeral sum K14 & 0.01 & 0.03 & 0.06 & 0.00\\
			 \hline
			 Entire sum K14 & 0.01 & 0.00 & 0.01 & 0.00\\
			 \hline
%			 K14 Mean & 0.02 & 0.04 & 0.03 & xx\\ [1ex]
%			 \hline
			Organoid size & 0.07 & 0.01 & \textbf{0.07} &  \textbf{0.06} \\
			 \hline
		\end{tabular}
		}
\end{table}

@@

\section{Discussion}
We implemented a method to quanitfy the invasive phenotypes organoids derived from two distinct mouse models, namely PyMT and C3(1)tag.\\
Out of the features we tested, we found that peripheral K14 expression correlated with the invasive phenotype.\\
Why is this important and/or interesting?\\
Future directions: Test our method on Patient derived organoids, PDOs.\\
Does organoid invasion score correlate with patient outcome?

\section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%

\end{comment}

\begin{thebibliography}{8}

>>>>

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% For commenting
\usepackage{comment}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Membrane-localized Keratin-14 Promotes Invasion} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Yohannes Tsehay\textsuperscript{1},
Hildur Knutsodottir\textsuperscript{1},
Andrei Kucharavy\textsuperscript{1\textcurrency},
Veena Padmanaban\textsuperscript{2},
Joel Bader\textsuperscript{1*}
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} High-Throughout Biology Center and Department of Biomedical Engineering, Johns Hopkins University, Baltimore, MD, USA
\\
\textbf{2} Center for Cell Dynamics and Department of Cell Biology, Johns Hopkins University School of Medicine, Baltimore, MD, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
%\ddag These authors also contributed equally to this work.

% Current address notes
\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* joel.bader@jhu.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Metastasis is the main predictor of outcome for patients with cancer, yet the molecular mechanism driving invasive phenotypes is not well under-stood, hindering development of assays and therapeutics for this stage of cancer progression. In this study, we characterize a molecular biomarker for invasion in greater detail, using an automated computer model. The model quantifies the invasive potential of tumors, allowing for quantification of even minor contributions to an invasive phenotype from individual genes, and can potentially be used to establish interactions among genes. Keratin 14 (K14) is a known molecular biomarker that is correlated with poor outcomes in breast cancer patients. We apply our automated computer model, which was built in Python, to test the hypothesis that K14 is directly correlated with automatically generated invasion scores, independent of tumor size. We used two different transgenic mice as our breast cancer tumor models. Organoids were generated from these mice, and each organoid had a corresponding differential interference contrast image, K14 image, and a boundary around the organoid drawn manually which was used to generate an invasion score for the organoid using our automated system. The parameters assessed include the following: entire K14 expression, peripheral K14 expression (edges of the organoid), central K14 expression (center of the organoid), and organoid size. Peripheral K14 expression showed the strongest correlation with invasion scores for both types of transgenic mice, suggesting that K14 expression in cells located in the periphery may be an important marker of invasion. This relationship was more prominent in one mouse model than the other, indicating that additional factors play a role in invasion and dissemination. In future studies, we plan to perform a similar analysis using human organoids generated from breast tumors.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

@@

%\begin{eqnarray}
%\label{eq:schemeP}
%	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- %H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
%\end{eqnarray}

\section*{Materials and methods}
\subsection*{Data acquisition}

@@

% For figure citations, please use "Fig" instead of "Figure".
% Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Results and Discussion can be combined.
\section*{Results}
% Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Image1.pdf}
\caption{Displays the K14 Image, DIC image, Bounday and spectral power analysis plots for three different organoids. \textcolor{red}{Axis font needs to be bigger. Y-axis in spectral score should all be the same and we can probably skip column 2.}} 
\label{fig1}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=\textwidth]{docs/01_paper/mouse_1_Day5_FA.pdf}
\caption{comment} 
\label{fig2}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{docs/01_paper/mouse_1_Day5_KPS.pdf}
\caption{comment} 
\label{fig3}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{docs/01_paper/mouse_1_Day5_KCS.pdf}
\caption{comment} 
\label{fig4}
\end{figure}

\begin{figure}[!h]
\includegraphics[width=\textwidth]{docs/01_paper/mouse_1_Day5_KS.pdf}
\caption{comment} 
\label{fig4}
\end{figure}

\begin{table}
\caption{{\bf Peripheral K14 explains correlates with invasive potential the best.}}
\label{tab1}
		\centering
		\resizebox{0.8\textwidth}{!}{
		 \begin{tabular}{||l c c c c||}
			\hline
			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
			 \hline
			 Organoids (PyMMT mice) & 	1 & 2 & 3 & 4 \\ [0.5ex]
			 \hline\hline
			  \textbf{Peripheral sum K14} & \textbf{0.39} & \textbf{0.43} & \textbf{0.29} & \textbf{0.123} \\
			 \hline
			 Centeral sum K14 & 0.21 & 0.19 & 0.11 & 0.010 \\
			 \hline
			 Entire sum K14 & 0.22 & 0.22 & 0.12 & 0.013 \\
			 \hline
%			 K14 Mean & 0.02 & 0.04 & 0.03 \\ [1ex]
%			 \hline
			Organoid size & 0.27 & 0.33 & 0.27 & 0.076 \\
			 \hline
		\end{tabular}
		}
\end{table}

\begin{table}
\caption{{\bf Peripheral K14 explains correlates with invasive potential the best.}}
\label{tab1}
		\centering
		\resizebox{0.8\textwidth}{!}{
		 \begin{tabular}{||l c c c c||}
			\hline
			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
			 \hline
			 Organoids (C3(1)tag mice) & 1 & 2 & 3 & 4  \\ [0.5ex]
			 \hline\hline
			  \textbf{Peripheral sum K14} & \textbf{0.11} & \textbf{0.25} & 0.06 & 0.03 \\
			 \hline
			 Centeral sum K14 & 0.01 & 0.03 & 0.06 & 0.00\\
			 \hline
			 Entire sum K14 & 0.01 & 0.00 & 0.01 & 0.00\\
			 \hline
%			 K14 Mean & 0.02 & 0.04 & 0.03 & xx\\ [1ex]
%			 \hline
			Organoid size & 0.07 & 0.01 & \textbf{0.07} &  \textbf{0.06} \\
			 \hline
		\end{tabular}
		}
\end{table}

@@

\begin{comment}
% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}
\end{comment}

%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
\subsubsection*{3rd level heading}

\begin{enumerate}
	\item{react}
	\item{diffuse free particles}
	\item{increment time by dt and go to 1}
\end{enumerate}

\section*{Discussion}
%Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero~\cite{bib3}.

We implemented a method to quanitfy the invasive phenotypes organoids derived from two distinct mouse models, namely PyMT and C3(1)tag.\\
Out of the features we tested, we found that peripheral K14 expression correlated with the invasive phenotype.\\
Why is this important and/or interesting?\\
Future directions: Test our method on Patient derived organoids, PDOs.\\
Does organoid invasion score correlate with patient outcome?

\section*{Conclusion}

\section*{Supporting information}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 File.}
\label{S1_File}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Video.}
\label{S1_Video}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Appendix.}
\label{S1_Appendix}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\nolinenumbers

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
% 
\begin{thebibliography}{10}
